{ \sffamily \LARGE Electronic supplementary material}\\{\bf \sffamily \LARGE Evolution of reciprocity with limited payoff memory

### 2024-03-14 paper/main.tex
cleaning main paper

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,setspace,enumitem,epsfig,titlesec,verbatim,color,array,eurosym,multirow}
\usepackage[sort&compress,comma,round,numbers]{natbib}
\usepackage[footnotesize,bf]{caption}
\usepackage[margin=2.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{blkarray}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{lineno}
% \linenumbers
\smallskip % Erlaubt kleine Abstaende zwischen Paragraphen, falls es dem Seitenlayout hilft
\renewcommand{\baselinestretch}{1.3}
\newcommand{\R}{\mathbb{R}}

@@

%% INTRO: Basic description of our model and our findings

To explore that question, we theoretically study imitation dynamics in the repeated prisoner's dilemma, using two extreme scenarios. 
The first scenario is the usual modeling approach. 
Here, individuals update their strategies based on their expected payoffs. 
We contrast this model with an alternative scenario where individuals update their strategies based on the very
last (one-shot) payoff they obtained. 
We find that individuals with limited payoff memory tend to adopt less generous strategies. 
Yet moderate levels of cooperation can still evolve. 
Moreover, as we increase the individuals' payoff memory to include the last two or three one-shot payoffs, cooperation rates quickly approach the rates observed in the classical baseline case.

%% INTRO: Summary and conclusions

% Overall, these findings suggest that while memory is important, already minimal payoff information may suffice for the evolution of direct reciprocity based on social learning. 
% They also suggest that the classical model of reciprocity (based on expected payoffs) can often be interpreted as a useful approximation to more realistic models that include cognitive constraints.

\todo{To address the reviewer's comment, we can either delete the last paragraph or rephrase the second-to-last paragraph as follows:}

To explore this question, we theoretically study imitation dynamics in the
repeated prisoner's dilemma, employing two extreme scenarios. In the first
scenario, which follows the conventional modeling approach, individuals update
their strategies based on their expected payoffs. We contrast this model with an
alternative scenario where individuals base their strategy updates solely on the
very last (one-shot) payoff they obtained. We observe that individuals with
limited payoff memory tend to adopt less generous strategies, yet moderate
levels of cooperation can still emerge. This suggests that while memory plays a
significant role, minimal payoff information may suffice for the evolution of
direct reciprocity through social learning. Moreover, increasing individuals'
payoff memory to include the last two or three one-shot payoffs leads to
cooperation rates quickly approaching those observed in the classical baseline
case. This implies that the classical reciprocity model, based on expected
payoffs, often serves as a useful approximation to more complex models
incorporating cognitive constraints.

>>>>

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,setspace,enumitem,epsfig,titlesec,verbatim,color,array,eurosym,multirow}
\usepackage[sort&compress,comma,round,numbers]{natbib}
\usepackage[footnotesize,bf]{caption}
\usepackage[margin=2.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{blkarray}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{lineno}
\linenumbers
\smallskip % Erlaubt kleine Abstaende zwischen Paragraphen, falls es dem Seitenlayout hilft
\renewcommand{\baselinestretch}{1.3}
\newcommand{\R}{\mathbb{R}}

@@

%% INTRO: Basic description of our model and our findings 
Suggestion one:
To explore that question, we theoretically study imitation dynamics in the repeated prisoner's dilemma, using two extreme scenarios. 
The first scenario is the usual modeling approach. 
Here, individuals update their strategies based on their expected payoffs. 
We contrast this model with an alternative scenario where individuals update their strategies based on the very
last (one-shot) payoff they obtained. 
We find that individuals with limited payoff memory tend to adopt less generous strategies. 
Yet moderate levels of cooperation can still evolve. 
Moreover, as we increase the individuals' payoff memory to include the last two or three one-shot payoffs, cooperation rates quickly approach the rates observed in the classical baseline case.

Suggestion two:
To explore this question, we theoretically study imitation dynamics in the
repeated prisoner's dilemma, employing two extreme scenarios. In the first
scenario, which follows the conventional modeling approach, individuals update
their strategies based on their expected payoffs. We contrast this model with an
alternative scenario where individuals base their strategy updates solely on the
very last (one-shot) payoff they obtained. We observe that individuals with
limited payoff memory tend to adopt less generous strategies, yet moderate
levels of cooperation can still emerge. This suggests that while memory plays a
significant role, minimal payoff information may suffice for the evolution of
direct reciprocity through social learning. Moreover, increasing individuals'
payoff memory to include the last two or three one-shot payoffs leads to
cooperation rates quickly approaching those observed in the classical baseline
case. This implies that the classical reciprocity model, based on expected
payoffs, often serves as a useful approximation to more complex models
incorporating cognitive constraints.
